How to Analyze Build Logs\\ ---\\ A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-03-03 tse-paper/abstract.tex
include loads of text and graphics from thesis, fix graphics, start adapting heading levels

Software builds from continuous integration produce detailed logs about the status and results of the various tools involved in the build.
These build logs are a valuable data source for developers and researchers to inspect test results, the duration of build steps or understand the cause of a build failure.
However, build logs are very verbose, at best semi-structured and their structure differs highly between projects.
This makes it hard to process and analyze them.
In this paper, we evaluate and compare three different techniques that aim to retrieve specified text chunks from a build log, namely program synthesis by example, textual similarity and search keywords.
We conduct an empirical study by comparing these techniques on the \emph{LogChunks} data set of 797 Travis CI logs from a diverse range of projects.
Our findings show that none of the three techniques clearly outperforms the others.
We discuss under which circumstances each technique performs best and provide a recommendation on when developers or researchers should use which technique.

>>>>

Build logs are textual by-products that a software build process
creates, often as part of its Continuous Integration (CI)
pipeline. Build logs are a paramount source of information for
developers when debugging into and understanding a build
failure. Recently, attempts to partly automate this time-consuming,
purely manual activity have come up, such as rule- or
information-retrieval-based techniques.

We evaluate and compare three different techniques that aim to retrieve
specified log parts (chunks) from a build log, namely program synthesis
by example, textual similarity and search keywords.
We conduct an empirical study by comparing these techniques on the manually
labeled \emph{LogChunks} data set.
Our findings show that none of the three techniques in general outperforms
the others. We discuss under which circumstances each technique performs best
and provide a recommendation on when developers or researchers should use which
technique.

% Software builds from continuous integration produce detailed logs about the status and results of the various tools involved in the build.
% These build logs are a valuable data source for developers and researchers to inspect test results, the duration of build steps or understand the cause of a build failure.
% However, build logs are very verbose, at best semi-structured and their structure differs highly between projects.
% This makes it hard to process and analyze them.
% In this paper, we evaluate and compare three different techniques that aim to retrieve specified text chunks from a build log, namely program synthesis by example, textual similarity and search keywords.
% We conduct an empirical study by comparing these techniques on the \emph{LogChunks} data set of 797 Travis CI logs from a diverse range of projects.
% Our findings show that none of the three techniques clearly outperforms the others.
% We discuss under which circumstances each technique performs best and provide a recommendation on when developers or researchers should use which technique.
